Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-04-01 journal-draft/bare_jrnl_comsoc.tex
minor changes in 5.3 and conclusion section

\subsection{Insights Obtained from the Simulation}
The simulation in the large CRN network confirms the conclusion made based on the simulation in the small CRN network, which is the average number of CCs along is not able to denote the robustness of the clusters, because the cluster size and the cluster members also affect the robustness.

@@

The shortcoming of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.

>>>>

\subsection{Insights Obtained from the Simulation}
The simulation in the large CRN network confirms the conclusion made based on the simulation in the small CRN network, which is that the average number of CCs along is not able to denote the robustness of the clusters, because the cluster size and the constitution of the cluster also affect the robustness.

@@

The limitation of distributed scheme ROSS is it doesn't generate clusters whose sizes exceed the cluster head's neighborhood.
The reason is with ROSS, cluster heads form clusters on the basis of their neighborhood, and don't involve the nodes which are outside the neighborhood.
In the other way around, forming big cluster which extends a cluster head's neighborhood has limited application scenarios, as multiple hop communication and coordination are required within these clusters.
